---
title: "Project1 Titanic story"
author: "Spencer Muncey and Chenchao Zang"
date: "September 15, 2015"
output: html_document
---
#RMS Titanic
The RMS Titanic began her maiden voyage on April 10, 1912 and sank to the bottom of the ocean after hitting an iceberg 5 days later. To learn more about the Titanic, you can visit this page on [Wikipedia](https://en.wikipedia.org/wiki/RMS_Titanic).

###Session Information
Before we get started with showing the plots, here is some information about how my RStudio is set up
```{r}
sessionInfo()
```
###The Dataset
The data set used to produce the following graphs contains information on almost 900 passengers of that fateful ship. Here is a subset and summary of that data:

```{r}
source("../01 Data/Titanic_DataFrame.R", echo = TRUE)
```
<!--This piece of R code loads the other two datasets that are needed to produce the visualizations for the plots -->
```{r, echo=FALSE}
source("../01 Data/Titanic_Age_Less_Ten.r", echo = FALSE)
source("../01 Data/Titanic_NoNullSex_df.r", echo = FALSE)
```

###Plot 1: Fare and Age of Titanic Passengers broken down by gender
```{r, fig.height=10, fig.width=10}
source("../02 Visualizations/Age_Fare_Sex.R", echo = TRUE)
```
Here is the R code used to produce this plot:
```
require(ggplot2)
ggplot(data=Titanic_df,aes(x=as.numeric(as.character(AGE)), y=as.numeric(as.character(FARE)), color=SEX)) + 
  coord_cartesian() + 
  scale_x_continuous() +
  scale_y_continuous() +
  labs(title='Titanic',x="Age", y=paste("Fare")) +
  geom_point(stat="identity",position=position_jitter(width=.3, height=0))
```
Here is the SQL statement used to produce this plot:
```
select * from Titanic;

```
###Plot 2: Fare and Age of Titanic Passengers broken down by gender with no null sex
```{r, fig.height=10, fig.width=10}
source("../02 Visualizations/Fare_Sex_Age_NoNull.R", echo = TRUE)
```

Here is the R code used to produce this plot:
```
require(ggplot2)
df<-Titanic_NoNullSex_df
ggplot(data=df,aes(x=as.numeric(as.character(AGE)), y=as.numeric(as.character(FARE)), color=SEX)) + 
  coord_cartesian() + 
  scale_x_continuous() +
  scale_y_continuous() +
  labs(title='Titanic',x="Age", y=paste("Fare")) +
  geom_point(stat="identity",position=position_jitter(width=.3, height=0))
```
Here is the SQL statement used to produce this plot:
```
select * from Titanic where SEX IS NOT NULL;

```
###Plot 3: Fare and Survival of Titanic Passengers broken down by gender
```{r, fig.height=10, fig.width=10}
source("../02 Visualizations/Fare_Survived_Character.R", echo = TRUE)
```

Here is the R code used to produce this plot:
```
require(ggplot2)
df<-Titanic_NoNullSex_df
ggplot(data=df,aes(x=SEX, y=as.numeric(as.character(FARE)), color=as.character(SURVIVED))) + 
  coord_cartesian() + 
  scale_x_discrete() +
  scale_y_continuous() +
  labs(title='Titanic',x="SURVIVED", y=paste("FARE")) +
  geom_point(stat="identity",position=position_jitter(width=.3, height=0))
```
Here is the SQL statement used to produce this plot:
```
select * from Titanic where SEX IS NOT NULL;

```
###Plot 4: Fare and Survival of Titanic Passengers broken down by gender and passenger class
```{r, fig.height=10, fig.width=10}
source("../02 Visualizations/Fare_Survived_Sex.R", echo = TRUE)
```

Here is the R code used to produce this plot:
```
require(extrafont)
ggplot() + 
  coord_cartesian() + 
  scale_x_discrete() +
  scale_y_continuous() +
  facet_grid(PCLASS~SURVIVED, labeller=label_both) +
  labs(title='Titanic') +
  labs(x="SURVIVED", y=paste("FARE")) +
  layer(data=Titanic_NoNullSex_df, 
        mapping=aes(x=as.character(SEX), y=as.numeric(as.character(FARE)), color=SEX), 
        stat="identity", 
        stat_params=list(), 
        geom="point",
        geom_params=list(), 
        position=position_jitter(width=0.3, height=0)
  )
```
Here is the SQL statement used to produce this plot:
```
select * from Titanic where SEX IS NOT NULL;

```
###Plot 5: Fare and Age of Titanic Passengers broken down by gender
```{r, fig.height=10, fig.width=10}
source("../02 Visualizations/Fare_Survived_Sex_Ten.r", echo = TRUE)
```
Here is the R code used to produce this plot:
```
require(extrafont)
ggplot() + 
  coord_cartesian() + 
  scale_x_discrete() +
  scale_y_continuous() +
  facet_grid(PCLASS~SURVIVED, labeller=label_both) +
  labs(title='Titanic where age <= 10') +
  labs(x="SURVIVED", y=paste("FARE")) +
  layer(data=Titanic_Age_Less_Ten_df, 
        mapping=aes(x=as.character(SEX), y=as.numeric(as.character(FARE)), color=SEX), 
        stat="identity", 
        stat_params=list(), 
        geom="point",
        geom_params=list(), 
        position=position_jitter(width=0.3, height=0)
  )
```
Here is the SQL statement used to produce this plot:
```
select * from Titanic where SEX IS NOT NULL AND AGE<=10;

```
###Plot 6: Fare charged by gender and passenger class (new interesting plot)
```{r, fig.height=10, fig.width=10}
source("../02 Visualizations/New_Interesting_plot.r", echo = TRUE)
```

Here is the R code used to produce this plot:
```
require(extrafont)
ggplot() + 
  coord_cartesian() + 
  scale_x_discrete() +
  scale_y_continuous() +
  facet_grid(.~PCLASS) +
  labs(title="Titanic fare's charged by class") +
  labs(x="Gender", y=paste("FARE")) +
  layer(data=Titanic_NoNullSex_df, 
        mapping=aes(x=SEX, y=as.numeric(as.character(FARE)), color=SEX), 
        stat="identity", 
        stat_params=list(), 
        geom="point",
        geom_params=list(), 
        position=position_jitter(width=0.3, height=0)
  )
```
Here is the SQL statement used to produce this plot:
```
select * from Titanic where SEX IS NOT NULL;

```
