---
title: "Project1 Titanic story"
author: "Spencer Muncey and Chenchao Zang"
date: "September 10, 2015"
output: html_document
---
#RMS Titanic
The RMS Titanic began her maiden voyage on April 10, 1912 and sank to the bottom of the ocean after hitting an iceberg 5 days later. To learn more about the Titanic, you can visit this page on [Wikipedia](https://en.wikipedia.org/wiki/RMS_Titanic).  
###Session Information
Before we get started with showing the plots, here is some information about how my RStudio is set up
```{r}
sessionInfo()
```
###The Dataset
The data set used to produce the following graphs contains information on almost 900 passengers of that fateful ship. Here is a subset and summary of that data:

```{r}
source("../01 Data/Titanic_DataFrame.R", echo = TRUE)
```
<!--This piece of R code loads the other two datasets that are needed to produce the visualizations for the plots -->
```{r, echo=FALSE}
source("../01 Data/Titanic_Age_Less_Ten.r", echo = FALSE)
source("../01 Data/Titanic_NoNullSex_df.r", echo = FALSE)
```

###Plot 1: Fare and Age of Titanic Passengers broken down by gender
```{r, fig.height=10, fig.width=10}
source("../02 Visualizations/Age_Fare_Sex.R", echo = TRUE)
```

###Plot 2: Fare and Age of Titanic Passengers broken down by gender with no null sex
```{r, fig.height=10, fig.width=10}
source("../02 Visualizations/Fare_Sex_Age_NoNull.R", echo = TRUE)
```

###Plot 3: Fare and Survival of Titanic Passengers broken down by gender
```{r, fig.height=10, fig.width=10}
source("../02 Visualizations/Fare_Survived_Character.R", echo = TRUE)
```

###Plot 4: Fare and Survival of Titanic Passengers broken down by gender and passenger class
```{r, fig.height=10, fig.width=10}
source("../02 Visualizations/Fare_Survived_Sex.R", echo = TRUE)
```

###Plot 5: Fare and Age of Titanic Passengers broken down by gender
```{r, fig.height=10, fig.width=10}
source("../02 Visualizations/Fare_Survived_Sex_Ten.r", echo = TRUE)
```

###Plot 6: Fare charged by gender and passenger class (new interesting plot)
```{r, fig.height=10, fig.width=10}
source("../02 Visualizations/New_Interesting_plot.r", echo = TRUE)
```
