---
title: "Project1 Titanic story"
author: "Spencer Muncey and Chenchao Zang"
date: "September 10, 2015"
output: html_document
---
The RMS Titanic began her maiden voyage on April 10, 1912 and sank to the bottom of the ocean after hitting an iceberg 5 days later. To learn more about the Titanic, you can visit this page on [Wikipedia](https://en.wikipedia.org/wiki/RMS_Titanic). 

The data set used to produce the following graphs contains information on almost 900 passengers of that fateful ship. Here is a subset of that data:

```{r, echo=FALSE, tidy=TRUE}
require("jsonlite")
require("RCurl")
# Change the USER and PASS below to be your UTEid
Titanic_df <- data.frame(fromJSON(getURL(URLencode('129.152.144.84:5001/rest/native/?query="select * from TITANIC"'),httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521/PDBF15DV.usuniversi01134.oraclecloud.internal', USER='cs329e_sm44585', PASS='orcl_sm44585', MODE='native_mode', MODEL='model', returnDimensions = 'False', returnFor = 'JSON'), verbose = TRUE), ))
summary(Titanic_df)
```

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
